Download data

### 2024-05-08 scripts/subsetDataforCrews.Rmd
rebuild project builder from the ground up

#### Process geographic data to a mask of the field office ####
focal_bbox <- dplyr::filter(admin_boundaries, ADMU_NA %in% stringr::str_to_upper(teams_list[[13]]$FieldOffice) ) %>%  
  sf::st_union() %>% 
  sf::st_transform(5070)

focal_bbox <- focal_bbox 
blm_surf_sub <- sf::st_intersection(blm_surf, focal_bbox)

ptest <- mask(ptest, blm_surf_sub)
ptest <- trim(ptest)
plot(ptest)

crew_dir <-  '/media/steppe/hdd/2024SOS_CrewGeospatial/Uncompahgre - P102085'
lapply(X = spp_needed_test[1], FUN = empiricalSTZ_writer, 
            seed_zones = seed_zones, pSTZs = ptest) # 24 pts, 245 polys

>>>>

#### Process geographic data to a mask of the field office ####
focal_bbox <- dplyr::filter(admin_boundaries, 
                            ADMU_NA %in% 
                              stringr::str_to_upper(teams_list[[13]]$FieldOffice)) %>%  
  sf::st_union() %>% 
  sf::st_transform(5070)

focal_bbox <- focal_bbox 
blm_surf_sub <- sf::st_intersection(blm_surf, focal_bbox) 
ptest <- mask(ptest, blm_surf_sub)

spp_needed_test <- filter(spp_needed, Requisition == 'Uncompahgre - P102085')

emp_prov_info <- identify_spp_emp_prov_sz(
  spp_needed_test, seed_zones = seed_zones, pSTZs = prov_stz, 
  focal_domain = focal_bbox, blm_surf_sub = blm_surf_sub)

crew_dir <-  '/media/steppe/hdd/2024SOS_CrewGeospatial/Uncompahgre - P102085'

# here we can put in:
taxa_w_provisional_stz <- split(emp_prov_info[["taxa_w_provisional_stz"]], 
                                f = 1:nrow(emp_prov_info[["taxa_w_provisional_stz"]]))

taxa_w_empirical_stz <- split(emp_prov_info[["taxa_w_empirical_stz"]], 
                                f = 1:nrow(emp_prov_info[["taxa_w_empirical_stz"]]))

lapply(X = spp_needed_test[3:10], FUN = provisionalSTZ_writer, 
            seed_zones = seed_zones, pSTZs = masked_pSTZ_lyr) 
p <- '/media/steppe/hdd/SDM_restorations/results/suitability_maps'
example_rast <- rast(file.path(p,'Achnatherum_hymenoides1k-2024-01-10_09:42:26.tif') )
prov_stz <- project(prov_stz, 'epsg:5070') 
prov_stz <- resample(prov_stz, example_rast)

lapply(teams_list[13], project_maker, 
       admu = admin_boundaries, 
       target_species = spp_needed, 
       blm_surf = blm_surf, 
       fs_surf = usfs_surf, 
       fire = fire_perimeters, 
       invasive = invasives, 
       total_change = change_intensity, 
       occurrences = occurrences, 
       roads = roads, 
       pSTZs = prov_stz,
       seed_transfer = STZ)
